Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-11-07 writing/ehp_introduction.tex
Make more edits

Recently, several major tropical cyclones have hit \ac{US} cities, including
Hurricanes Harvey, Irma, and Maria in 2017 \parencite{blake20182017} and
Hurricanes Florence and Michael in 2018 \parencite{avila20192018}. Researchers
are exploring how these storms impacted human health (e.g.,
\parencite{santos2018use, rivera2018estimating, santos2018differential,
grineski2019impact, issa2018deaths, tanz2019notes, paul2019brief}), including
through projects funded through \ac{NIH} Rapid Response grants
\parencite{nihreporter}. These projects will add to evidence from previous
hurricanes, including Sandy in 2012 (e.g., \parencite{swerdel2014}) and Katrina
in 2005 (e.g., \parencite{burton2009health}), characterizing the health impacts
of hurricanes.

A recent review highlights the need to supplement these single-storm studies
with multi-year, multi-storm studies, to identify patterns that are common
across multiple storms [ref]. While multi-year studies of hurriance mortality
impacts have been conducted using disaster surveillance data, studies based on
administrative data could identify risks for non-accidental mortality and
morbidity that those studies likely undercount [ref]. Multi-storm studies with
administrative data require exposure assessment that is consistent across time
and space, allowing the administrative data to be linked to disaster exposure
[ref]. Key to expanding tropical cyclone epidemiology are therefore exposure
assessment methods that appropriately capture hazards of the storm that are
relevant to human health, methods that can be applied consistently across
multiple storms, locations, and years.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's
\underline{minimum pressure} and \underline{central maximum sustained winds}. This data is openly
available through the \ac{HURDAT2}, a post-storm assessment conducted
by the \ac{US} \ac{NHC} that incorporates data from a variety of sources,
including satellite data and, when available, aircraft reconnaissance
data~\parencite{landsea2013, jarvinen1988}. With this data, it is
straightforward to measure whether a community was in the direct path, or
within a certain distance of the path, of a storm. Some studies have indeed
used this data to assess tropical cyclone exposure based on how near the
storm's central track came to the county, either to assess average exposure
patterns to tropical storms [refs] or to characterize exposure for health
studies [refs].

When epidemiological studies assess exposure to a tropical cyclone based on 
how close the storm came to a community, however, they may misclassify exposure. 
Tropical cyclones vary dramatically in size: \ac{US} tropical
cyclones have been observed with radii to maximum winds as small
as~20~\si{\kilo\metre} and as large
as~200~\si{\kilo\metre}~\parencite{mallin2006, quiring2011variations}.  While a
number of tropical cyclone hazards are strongly associated with distance from
the tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.

Further, when studies use distance from the storm's track to assess exposure,
they often use an equal buffer distance on each side of the tropical cyclone
track (e.g.,~\cite{czajkowski2011, grabich2015, grabich2016, zandbergen2009,
tansel2010}). However, the forces of a tropical cyclone tend to be distributed
around the center in a non-symmetrical way. Extreme winds are more common to
the right of the track, where counter-clockwise cyclonic winds move in concert
with the tropical cyclone's forward motion~\parencite{halverson2015}, and the
fatal tornadoes associated with \ac{US} tropical cyclones between~1995 and~2009
occurred almost exclusively to the right of the tropical cyclone's track,
mostly in the right front quadrant of the tropical
cyclone~\parencite{moore2012}. Rain, conversely, is often heaviest to the left
of the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\parencite{atallah2003, atallah2007,
zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.

If a study misclassifies exposure to the hazard or hazards that cause the
health risk being studied, the study will generate biased estimates of tropical
cyclone risks and impacts. Further, when different studies use different
methods to assess exposure to tropical cyclones, their results are difficult to
meaningfully compare and aggregate. If different methods identify
similar sets of communities as ``exposed'',  these concerns are less serious.
However, if different methods differ substantially in which communities they
identify as ``exposed'', it makes it very important that epidemiological
studies are thoughtful in how they assess exposure.

To provide open-source data on tropical cyclone exposures to other researchers,
we developed a dataset of county-level exposure to tropical cyclones in all
eastern \ac{US} counties for five different metrics
(Table~\ref{tab:exposuremetrics}): (1)~distance to tropical cyclone track;
(2)~maximum sustained wind speed; (3)~cumulative rainfall; (4)~flood events;
and (5)~tornado events~\parencite{hurricaneexposure}. This data is provided at
the county level since data on many potential impacts are available at
county-level aggregations (e.g., direct hurricane-related
deaths~\parencite{czajkowski2011}; birth outcomes~\parencite{grabich2015,
grabich2016}; autism prevalence~\parencite{kinney2008}) and since decisions and
policies to prepare for, and respond to, tropical cyclones are often undertaken
at the county level~\parencite{zandbergen2009, rappaport2000}. Further, we
explored patterns in these exposure assessments across storm hazards and
measured how well exposure classification agreed across these five metrics in
terms of classifying specific counties as exposed to a tropical cyclone.

>>>>

Recently, several major tropical cyclones have hit \ac{US} cities, including
Hurricanes Harvey, Irma, and Maria in 2017~\parencite{blake20182017} and
Hurricanes Florence and Michael in 2018 \parencite{avila20192018}. Researchers
are exploring how these storms impacted human health
(e.g.,~\cite{santos2018use, rivera2018estimating, santos2018differential,
grineski2019impact, issa2018deaths, tanz2019notes, paul2019brief}), including
through projects funded by \ac{NIH} Rapid Response
grants~\parencite{nihreporter}. These projects will add to evidence
characterizing how hurricanes impact human health, including evidence from
multi-year studies based on fatality data from post-disaster
surveillance~\parencite{rappaport2000, rappaport2014fatalities,
rappaport2016fatalities, czajkowski2010fatal, czajkowski2011, moore2012}.

For several types of climate-related disasters---including heat waves, floods,
and wildfires---research based on post-disaster surveillance data has been
richly supplemented by studies analyzing trends in community-wide
administrative or vital data, including time series or case-crossover studies
(e.g.,~\cite{anderson2010heat, son2012impact, haikerwal2015impact,
liu2017wildfire, milojevic2017mental}).  These studies typically compare the
rate of a health outcome in a community during a disaster or disasters to rates
during comparable non-disaster periods.  While these studies cannot attribute
specific cases (e.g., a specific person's death) to a disaster, they can help
characterize the community-wide change in health risk during disasters, and can
help capture impacts that might be missed or underestimated in post-disaster
surveillance.  In many cases, these studies analyze multi-year, multi-community
data, allowing them to estimate average associations over many disasters and to
explore how a disaster's characteristics, or the characteristics of the
community it hits, modify associated health risk (e.g.,~\cite{anderson2010heat,
son2012impact, liu2017wildfire}).  Some studies have begun to use this approach
to study the health impacts of tropical cyclones, including several studies of
Hurricane Maria (e.g.,~\cite{santos2018use, santos2018differential}), Hurricane
Sandy (e.g.,~\cite{kim2016, mongin2017, swerdel2014}), and the 2004 hurricane
season in Florida~\parencite{mckinney2011}.  However, to expand this approach
to study longer time periods for large sets of communities, researchers must be
able to assess exposure to tropical cyclones consistently and comparably across
storms, years, and communities.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's minimum
central pressure and maximum wind speed.  This data is openly available through
the \ac{HURDAT2}, a post-storm assessment that incorporates data from several
sources, including satellite data and, when available, aircraft reconnaissance
data~\parencite{landsea2013, jarvinen1988}.  With this data, it is
straightforward to measure whether a community was in the direct path, or
within a certain distance of the path, of a storm. Some studies have indeed
used this data within epidemiological studies to assess tropical cyclone
exposure based on whether a storm's track passed through a community or how
near the storm's central track came to the community (e.g.,~\cite{currie2013,
kinney2008, caillouet2008increase}).

When epidemiological studies assess exposure to a tropical cyclone using, as a
proxy measurement, how close the storm came to a community, they may
misclassify exposure~\parencite{grabich2015measuring}. While a number of
tropical cyclone hazards are strongly associated with distance from the
tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like heavy rainfall,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.  Further, when studies use
distance from the storm's track to assess exposure, they often use the same
buffer constraints on each side of the tropical cyclone track
(e.g.,~\cite{czajkowski2011, kinney2008, currie2013}).  However, the forces of
a tropical cyclone tend to be distributed around its center non-symmetrically.
Extreme winds are more common to the track's right, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward
motion~\parencite{halverson2015}, and almost all of the fatal tornadoes
associated with \ac{US} tropical cyclones between~1995 and~2009 occurred to the
right of the tropical cyclone's track, mostly in the storm's right front
quadrant~\parencite{moore2012}. Rain, conversely, is often heaviest to the left
of the track, especially when the tropical cyclone interacts with other weather
systems~\parencite{atallah2003, atallah2007, zhu2013variations} or undergoes an
extratropical transition~\parencite{elsberry2002}.

The multi-hazard nature of tropical cyclones therefore makes it hard to assess
exposure based on how close the storm's central
track came to the community.  While other approaches have been developed to
incorporate storm hazards, particulary wind, into exposure assessment (e.g.,
\cite{grabich2015measuring, zandbergen2009, czajkowski2011}), there is not yet
a standard approach, and when different studies use different datasets or storm
hazards when assessing storm exposure, it becomes difficult to compare and
aggregate findings from different studies.

To help epidemiological researchers assess exposure to tropical cyclones, we
developed an open-source dataset~\parencite{hurricaneexposure}.  These data
cover all counties in states in the eastern half of the \ac{US} over multiple
years and include five metrics characterizing exposure to tropical cyclones
(Table~\ref{tab:exposuremetrics}): (1)~closest distance the storm's central
track came to the county's center (a proxy measurement of storm exposure used
in some previous studies); (2)~maximum sustained wind speed at the county's
center over the course of the storm; (3)~cumulative rainfall in the county over
the course of the storm; (4)~flood events in the county associated with the
storm; and (5)~tornado events in the county associated with the storm.  We
aggregated these data at the county level since data on many potential impacts
are available at county-level aggregations (e.g., direct hurricane-related
deaths~\parencite{czajkowski2011}; birth outcomes~\parencite{grabich2015,
grabich2015measuring}; autism prevalence~\parencite{kinney2008}) and since
decisions and policies to prepare for, and respond to, tropical cyclones are
often undertaken at the county level~\parencite{zandbergen2009, rappaport2000}.
We also wrote functions to explore and map this data and to link it
with county-level health data~\parencite{hurricaneexposuredata}

Here, we describe how we developed this dataset and explore how its
measurements compare to other data that could be used to characterize tropical
cyclone hazards in the context of epidemiological research. \textit{Further, we expand
on previous research that found large differences in which communities are
assessed as exposed to a tropical cyclone depending on whether exposure
assessment is based on distance to the storm's track or if it uses a metric
incorporating storm-related winds within the county during the storm,
concluding that a study may be prone to bias from exposure misclassification if
distance to the storm track is used as a proxy measurement for exposure
assessment~\parencite{grabich2015measuring}.}  The previous study investigated
this question for one hurricane season in Florida. Here we expand to
investigate this question across all counties in states in the eastern half of
the \ac{US} over multiple storms and years.  Further, we investigate patterns
in exposure classification based on other metrics of storm-related
hazards---rainfall, flooding, and tornadoes---that are important to characterize to
improve understanding of the inland health impacts of tropical
cyclones~\parencite{czajkowski2011, moore2012}. These results can help
epidemiologists design studies and plan statistical analysis for
multi-year, multi-community studies that investigate changes in community-wide
rates of health outcomes during exposure to the hazards brought by tropical
cyclones, including counties inland from a storm's landfall.

### 2019-11-07 writing/ehp_methods.tex
Make more edits

We aggregated data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}) as of the~2010 \ac{US} Decennial Census and for
all tracked land-falling or near-land Atlantic-basin tropical cyclones
between~1988 and~2015---all 136 storms in \ac{HURDAT2} \parencite{landsea2013}
that came within~250 \si{\kilo\metre} of at least one eastern \ac{US} county in
this period (Figure~\ref{fig:hurrtracks}).

@@

In the open-source data~\parencite{hurricaneexposuredata}, we provide daily
precipitation values for each county for the period from five days before to
three days after each storm's closest approach to the county.  In the software
that we published in association with this data~\parencite{hurricaneexposure},
we provide functionality to aggregate these daily values to create cumulative
precipitation estimates for custom windows around the date of the storm's
closest approach to the county. For example, a user could determine
precipitation only on the day the storm was closest to each county, but could
also determine the cumulative rainfall for a more extended period, like from
three days before to three days after the storm's closest approach. For the
analysis of binary exposure classifications in this study, we calculated
storm-associated rainfall as the sum of precipitation from two days before the
storm's closest approach to the county to one day after.

@@

To create a dataset of county-level maximum sustained winds during historical
tropical cyclones, we modeled maximum sustained wind speeds at each county's
population mean center~\parencite{countycenters} using a wind speed model based
on results from Willoughby~\parencite{willoughby2006parametric}. For each
storm, we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period, using a double exponential wind speed model with
inputs for the storm's forward speed, direction, and maximum wind
speed~\parencite{willoughby2006parametric, stormwindmodel}. This model
incorporates the asymmetry in wind speeds around the tropical cyclone center
that results from the storm's forward movement~\parencite{phadke2003modeling,
stormwindmodel}. We then identified the maximum sustained surface wind speed in
each county during each storm.

@@

For each tropical cyclone, we identified all events with event types related to
flooding (``Flood,'' ``Flash Flood,'' ``Coastal Flood'') and tornadoes
(``Tornado'') with a start date within a five-day window centered on the date
of the tropical cyclone's closest approach to the
county~\parencite{hurricaneexposuredata}. To exclude events that started near
in time to the storm but far from the storm's track, and so were likely
unrelated to the storm, we exculed any events that occurred outside~500
\si{\kilo\metre} of the tropical cyclone's track. ``Flood,'' ``Flash Flood,''
and ``Tornado'' events in this database were reported by county \ac{FIPS} code
and so could be directly linked to counties.  ``Coastal Flood'' events were
reported by forecast zone; for these, the event was matched to the appropriate
county if possible using regular expression matching of listed county
names~\parencite{noaastormevents}.

@@

For the rainfall metric, a distance constraint was also necessary, to ensure
that rainfall unrelated and far from the storm track were not misattributed to a
storm. Through exploratory analysis, we set this distance metric at~500
\si{\kilo\metre} (i.e., for a county to be classified as exposed based on
rainfall, the cumulative rainfall in the county had to be over the
75~\si{\milli\metre} threshold and the storm must have passed within~500
\si{\kilo\metre} of the county; Table~\ref{tab:exposuremetrics}). This distance
constraint was typically large enough to capture storm-related rain.  However,
data users should note that in rare cases---for example, exceptionally large
storms (e.g., Hurricane Ike in 2008) or storms for which storm tracking was
stopped at extratropical transition (e.g., Tropical Storm Lee in 2011)---some
storm-related rain exposures may be missed because of this distance constraint
(Figure~S1). This distance constraint can be customized using the software
published in association with the open-source
data~\parencite{hurricaneexposure}.

We characterized patterns in county-level exposure in the eastern \ac{US} for
exposure assessment based on each of the measured tropical cyclone hazards
(cumulative precipitation, maximum sustained winds, flooding, and tornadoes).
Depending on available exposure data, this assessment included some or all of
the period from~1988 to~2015 (Table 1). For each binary metric of exposure to a
tropical cyclone hazard, we first summed the total number of county-level
exposures over available years and mapped patterns in
these exposures. We next investigated agreement between storm exposure
classifications based on these different single-hazard exposures, as well as
between each of these and a distance-based proxy assessment of tropical cyclone
exposure (Table~\ref{tab:exposuremetrics}). We calculated the within-storm
Jaccard index~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. The Jaccard index~($J_s$) measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We measured these values for all study storms that affected a
large number of eastern \ac{US} counties (those storms with 100 or more
counties were classified as exposed by at least one of the exposure metrics)
during the years when all exposure data were available (1996\,--\,2011).

\subsection*{Case study}

The societal impact of a disaster depends both on its geophysical forces and on
the vulnerability of those living in the geographical areas it
affects~\parencite{chakraborty2005population, anderson2003community,
cutter1996vulnerability}. An estimate of ``physical exposure''---which
...---can help to jointly capture these facets of disaster impacts [ref, maybe
the peduzzi one given below?]. As a case study, we measured physical exposure
based on each metric of exposure and investigated whether conclusions from
these assessments varied substantially.

We collected data on the number of electricity-dependent Medicare beneficiaries
in each study county from the \ac{US} Department of Health \& Human Service's
emPower Map~2.0~\parencite{empower}. This subpopulation was selected because it
may be particularly susceptible to health impacts from tropical cyclone
exposure, especially through the pathway of storm-associated power outages and
evacuations. We calculated the physical exposure of the electricity-dependent
Medicare population in each county, based on tropical cyclone assessments using
each exposure metric (Table~\ref{tab:exposuremetrics}), following
\citeauthor*{peduzzi2009assessing}~(\citeyear{peduzzi2009assessing}):

\begin{equation}
E_c = F_c * P_c
\end{equation}

\noindent where~$E_c$ is the average yearly physical exposure among
electricity-dependent Medicare beneficiaries in county~$c$ to tropical cyclone
exposures based on a given metric,~$F_c$ is the estimated yearly expected
frequency of tropical cyclone exposures in county~$c$ based on that metric,
and~$P_c$ is the electricity-dependent Medicare population in
county~$c$, as of July~2017.

>>>>

We aggregated data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}) as of the~2010 \ac{US} Decennial Census. We
included all tracked land-falling or near-land Atlantic-basin tropical cyclones
between~1988 and~2015 by covering all 136 storms in \ac{HURDAT2}
\parencite{landsea2013} that came within~250 \si{\kilo\metre} of at least one
eastern \ac{US} county in this period (Figure~\ref{fig:hurrtracks}).

@@

In the open-source data~\parencite{hurricaneexposuredata}, we provide
precipitation values at a daily resolution for each county for the period from
five days before to three days after each storm's closest approach to the
county.  In the software that we published in association with this
data~\parencite{hurricaneexposure}, we provide functionality to aggregate these
daily values to create cumulative precipitation estimates for custom windows
around the date of the storm's closest approach to the county. For example, a
user could determine precipitation only on the day the storm was closest to
each county, but could also determine the cumulative rainfall for a more
extended period, like from three days before to three days after the storm's
closest approach. For the analysis of binary exposure classifications in this
study, we calculated storm-associated rainfall as the sum of precipitation from
two days before the storm's closest approach to the county to one day after.

@@

To create a dataset of county-level maximum sustained winds during historical
tropical cyclones, we modeled maximum sustained wind speeds at each county's
population mean center~\parencite{countycenters} using a wind speed model based
on results from Willoughby~\parencite{willoughby2006parametric}. For each
storm, we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period. We used a double exponential wind speed model with
inputs for the storm's forward speed, direction, and maximum wind
speed~\parencite{willoughby2006parametric, stormwindmodel}, incorporating the
asymmetry in wind speeds around the tropical cyclone center that results from
the storm's forward movement~\parencite{phadke2003modeling}. From these
15-\si{\minute} interval estimates, we identified the maximum sustained surface
wind speed in each county during each storm.

@@

For each tropical cyclone, we identified all events with event types related to
flooding (``Flood,'' ``Flash Flood,'' ``Coastal Flood'') or tornadoes
(``Tornado'') with a start date within a five-day window centered on the date
of the tropical cyclone's closest approach to the
county~\parencite{hurricaneexposuredata}. To exclude events that started near
in time to the storm but far from the storm's track, and so were likely
unrelated to the storm, we excluded any events that occurred~$\ge$500
\si{\kilo\metre} from the tropical cyclone's track. ``Flood,'' ``Flash Flood,''
and ``Tornado'' events in this database were reported by county \ac{FIPS} code
and so could be directly linked to counties.  ``Coastal Flood'' events were
reported by forecast zone; for these, the event was matched to the appropriate
county if possible using regular expression matching of listed county
names~\parencite{noaastormevents}.

@@

For the rainfall metric, a distance constraint was also necessary, to ensure
that rainfall unrelated and far from the storm track was not misattributed to a
storm. Through exploratory analysis, we set this distance metric at~500
\si{\kilo\metre} (i.e., for a county to be classified as exposed based on
rainfall, the cumulative rainfall in the county had to be over the
75~\si{\milli\metre} threshold and the storm must have passed within~500
\si{\kilo\metre} of the county; Table~\ref{tab:exposuremetrics}). This distance
constraint was typically large enough to capture storm-related rain.  However,
data users should note that in rare cases---for example, exceptionally large
storms (e.g., Hurricane Ike in 2008) or storms for which storm tracking was
stopped at extratropical transition (e.g., Tropical Storm Lee in 2011)---some
storm-related rain exposures may be missed because of this distance constraint
(Figure~S1). This distance constraint can be customized using the software
published in association with the open-source
data~\parencite{hurricaneexposure}.

We characterized patterns in county-level exposure in the eastern \ac{US} for
exposure assessment based on each of the measured tropical cyclone hazards
(cumulative precipitation, maximum sustained winds, flooding, and tornadoes).
Depending on available exposure data, this assessment included some or all of
the period from~1988 to~2015 (Table 1). For each binary metric of exposure to a
tropical cyclone hazard, we first summed the total number of county-level
exposures over available years and mapped patterns in
these exposures.

\textit{We next investigated agreement between storm exposure
classifications based on these different single-hazard exposures, as well as
between each of these and a distance-based proxy assessment of tropical cyclone
exposure.} We calculated the within-storm
Jaccard index~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. The Jaccard index~($J_s$) measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We measured these values for all study storms that affected a
large number of eastern \ac{US} counties (those storms with 100 or more
counties classified as exposed by at least one of the exposure metrics)
during the years when all exposure data were available (1996\,--\,2011).
